Bayesian Exploration in Deep Reinforcement Learning

### 2022-07-24 papers/CDRL/sample_paper.tex
TEMPORARY DEPLOY COMMIT

\begin{abstract}
  The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
  both left and right-hand margins. Use 10~point type, with a vertical
  spacing of 11~points. The \textbf{Abstract} heading must be centered,
  bold, and in point size 12. Two line spaces precede the
  Abstract. The Abstract must be limited to one paragraph.
\end{abstract}

>>>>

\begin{abstract}
  % The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
  % both left and right-hand margins. Use 10~point type, with a vertical
  % spacing of 11~points. The \textbf{Abstract} heading must be centered,
  % bold, and in point size 12. Two line spaces precede the
  % Abstract. The Abstract must be limited to one paragraph.
\end{abstract}
